\section{Common applications}
\label{sec:task}

This chapter will highlight some of the pieces of software we will be taking a look at, and why that software specifically. \\\\

Lets first take some common applications and categories. Some common pieces of software with examples are: spreadsheet software (excel), a form of browser (google chrome), a form of game launcher (steam), a game (destiny), document writing (word) and social communication (discord/teams). The examples are not the most common applications, but will give some recognition of the category.\\

Now let's look for the most common applications among those categories. 

\subsection{Spreadsheet software}
Sadly, it is not easy to find what type of spreadsheet software is the most common, there is little data of this out there. So for software alike this, we turn to google trends. Where the search frequency will decide how much it is used. This is an inherently flawed method, but will do. 

As according to it, Excel is the most popular, with a ratio of about 90 - 10 between excel and google sheets. Those 2 being the most frequently used \cite{Googletrend1}. So the first application will be Excel.

\subsection{Browser}
There is more info on this. The currently most popular browser is google chrome \cite{Statcounter1}. It comes pre-installed with many operating systems and is a fine way to access the internet. 

\subsection{Game launcher}
Steam still remains a market leader, due to convenient service and a user friendly client most likely. It still leads in sales and active users \cite{Statistica1}.

\subsection{Game}
There are games which are popular and outside of steam. But for shear convenience, the game will be chosen from steam. This is due to the fact that it has open data on the active player count on every game. This will tell us that the game with the highest active player count is Counter-Strike 2 at around 900k concurrent players \cite{Steamdb1}. Counter-Strike 2 is a multi-player team versus team game.  

\subsection{Document writing}
This is another topic with minimal data on it, so we turn to google trends again. Where it proclaims \cite{Googletrend2} that word is currently the most popular piece of document writing software.

\subsection{Social communication}
This time, according to google trends. There is no outright winner. None out of zoom, discord and teams have a winner which wins by above 10\% \cite{Googletrend3}. But, currently discord does win by a hair. Meaning that it will be chosen.
